Lnc34a CAGE

### 2017-12-10 inst/lnc34a_cage/lnc34a_cage.Rmd
trying to fix str_replace missing error in lnc34a_cage

packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject",
    "ggthemes",
    "printr"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

>>>>

packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject",
    "ggthemes",
    "printr",
    "stringr"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)
